%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%%
%%
%% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%%
%%
\documentclass[preprint,12pt,3p]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}


\journal{Neural Networks}

\begin{document}

\begin{frontmatter}

\title{Sample article to present \texttt{elsarticle} class\tnoteref{label0}}
\tnotetext[label0]{This is only an example}


\author[label1,label2]{Author One\corref{cor1}\fnref{label3}}
\address[label1]{Address One}
\address[label2]{Address Two\fnref{label4}}

\cortext[cor1]{I am corresponding author}
\fntext[label3]{I also want to inform about\ldots}
\fntext[label4]{Small city}

\ead{author.one@mail.com}
\ead[url]{author-one-homepage.com}

\author[label5]{Author Two}
\address[label5]{Some University}
\ead{author.two@mail.com}

\author[label1,label5]{Author Three}
\ead{author.three@mail.com}

\begin{abstract}
Text of abstract. Text of abstract. Text of abstract. Text of abstract. Text of abstract. 
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
foraging \sep active learning \sep template
%% MSC codes here, in the form: \MSC code \sep code
 or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

%% main text
\section{Introduction}
\label{sec:intro}

\begin{enumerate}
\item Why did I do the work?
	Robots exploring the world right now either depend highly on their controllers to give them objectives or they are planning with some global knowledge.  Operating in these kinds of conditions puts constraints on robot exploration opterations by relying on either humans to make decisions or a significant amount of scouting.

	Relying on humans to make decisions means that remote operators require considerable bandwidth to acquire sufficient situational awareness.  Conducting sufficient reconnaissance to make good decisions often obviates the need to send a robotic agent.

	What is lacking in the literature are robots that make decisions about what to investigate \emph{in situ} without reliance on humans and without necessarily having global knowledge.
	\item What were the central motivations and hypotheses?
	Animals, e.g. human geologists, make decisions about investigating phenomena in the world without necessarily having access to high resolution satellite imagery.  Despite this lack they are able to chose between sampling from materials in front of them and moving on to determine more profitable sampling locations.

	While these decisions may not be globally optimal they do demonstrate an ability that is lacking from exploration robots: to make decisions to stop and engage with the environment or to continue travelling in the hopes of finding more informative sampling locations.
	\end{enumerate}


\section{Background}
\label{sec:background}

	- Previous work in robotic exploration is either dependent on global information or it does not make reasoned decisions about the rest of the world and the sampling opportunities that are immediately available to it.
			- opportunistic science only takes advantage of what is immediately availble to the robot and with surplus sampling budget.
			- whoi and mbari follow set patterns (which is fine, the lawnmower is a good and noble thing) but they use an arbitrary threshold to make the decision to sample or not.  They do not take into account the rest of the environment.

	Who else has done what?

	- Work in the 1970's about foraging.  About making value judgements.
		- Key point from Charnov's work is that there has to be diminishing returns
		for extracting from a field (specifically towards an asymptote)
		- Different from our setting is that diminishing your reward in one area 
		contributes to diminishing your reward elsewhere. It isn't like picking
		apples off one tree, and finding a new tree with unpicked apples.

- Evidence that humans make (approximately) rational decisions (we over and under estimate low and high probabilities)

	- Design of experiments has led to (amongst other things) multi-armed bandit models of sequential experiment design.
	- See also maximum entropy sampling
	- See also mutual information sampling.
- Also consider active learning solutions (they all end up being the same anyway)

	- Robotics research has made robots that conduct exploration, but the only ones that make decisions about whether to investigate something or not do one of three things:
	1. match templates.
	2. seek improbable things.
	3. Engage in opportunistic science - they do something if they have the time.  They don't override human mission objectives.

	1 and 2 say nothing about the information content of the material under investigation.
	3 does not have the level of autonomy that we need for truly long-term or remote operations.

	How?

	What have we previously done:
	- D.R. Thompson's work
	- Only looking at satellite imagery.  Good but not sufficient.
	- Trey's work
	- Using POMDPs not scalable to a planet.
	- Mine. Where does my previous work fall short?
- Not bayesian (not a big deal?)
	- Still has the problem on knowing the number of sampling opportunities remaining.

	- Piroli 1999 - has come up with a very similar formulation as the one that 
		Mike and I came up with.
		- Something to consider is that we only get to take one sample per patch 
			because of science differentiation requirements (i.e. RP can't have 
			samples closer than 10cm to each other, maybe as far as 1m)
		- We could also incorporate the different cost it takes to identify things 
			in the scene.
		- We also have different times between patches.
		- Should it come to multiple contexts then we have the contextual bandit 
			problem
				- This means that we could keep different distributions of classes per 
					environment.


	%\input{background}
	%\input{background2}


\section{Method}
\label{sec:method}

	- figure method.1: An example of a path the rover might be following with sampling opportunities on it.  Changes over time. i.e. do two or more pictures showing how things change over time.
	- figure method.2: The reward function as samples are given to it, for two or three different distributions.
	- figure method.3: texture cam, raw image and texture labelled image.

	The experiment builds on prior work.  

	- The reward for sampling a class is an analog for the definition of surprise as defined by the Koch et al {cite papers}.  Koch looked at the change in the distribution that resulted in a Bayesian update.  Because this work uses a non-parametric kernel density estimation we compare $\frac{p(x|D\cup{x})}{p(x|D)}$

	- Combining foraging models with bandit literature 
		- The previous work on foraging assumed an inherent value to
			options that the agent cared about.  Specifically, energy stored up.
		- We use a valuation model taken from bandit literature.  
		- We use the reward function from Koch's attention models
		- We use the decision making process from foraging. 
		- We add the concept of multi-arrival rate things, awareness of time limits.
	- Previous work had a limit on the number of samples it could take
		- We realized that the actual quantity that limits the exploration process
			is time.
		- By limiting the time and (in this case) relaxing the limit on sample sizes
			we more accurately deal with productivity.  
	- This experiment models a type of prospecting where the number of samples isn't limited but they do take time. 
	- To that end we are looking at productivity.

	-  This experiment is more akin to contextual bandits.  
	- The image represents a context, the NIRVSS 
	- Apply texturecam classification of a scene, as the context
	- the choice is to sample or continue

	- Productivity 


\section{Results}
\label{sec:results}


- Figure results.1: Overall error at the end of the trial with unlimited sampling and without weighing by the rarity (1/prob of occurrence) of the class
- Figure results.2: overall error at the end of the trial with unlimited sampling and with weighing by the rarity of the class
- Figure results.3: Overall performance when combining limited time and limited sample budgets.

\section{Conclusion}
\label{sec:conclusion}

	%% The Appendices part is started with the command \appendix;
	%% appendix sections are then done as normal sections
\appendix

\section{Section in Appendix}
\label{appendix-sec1}

	Sample text. Sample text. Sample text. Sample text. Sample text. Sample text. 
	Sample text. Sample text. Sample text. Sample text. Sample text. Sample text. 
	Sample text. 

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}         ==>>  [#]
%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
%%

%% References with bibTeX database:

\bibliographystyle{elsarticle-num}


\bibliography{merged}


\end{document}

%%
%% End of file `elsarticle-template-num.tex'.

